An investigation into using scagnostics to find interesting projections of high-dimensional data

### 2018-10-29 scagnostics.Rmd
Summary table updated.
Some comments.

\textcolor{red}{What is upper bound of TIC as function of sample size? If we define $n' = n^{0.6}$, rounded to integer values only, can we calculate it as $TIC_{max} = 2 \sum_{i=1}^{n'} \frac{n'}{i}$, keeping in mind that each entry of the characteristic matrix should be between [0,1]. Each entry in the sum should be rounded also, only integer number of bins enter actual calculation, so this should be approximation only.}

@@

@@

\begin{table}
\begin{center}
\caption{Summary}
\label{tab:summary}
\begin{tabular}{|l|c|c|c|c|}
\hline
Index & smooth & rotation invariant & fast & general \\
\hline
Convex & ! & ! & \checkmark & ! \\
Skinny & ! & ! & \checkmark & ! \\
Stringy & $\times$ & ! & \checkmark & ! \\
\hline
splines2D & \checkmark & $\times$ & \checkmark & ! \\
dcor2D & \checkmark & $\times$ & ! & ! \\
\hline
MINE & ! & ! & ! & \checkmark\\
\hline
\end{tabular}
\end{center}
\end{table}

>>>>

\textcolor{red}{What is upper bound of TIC as function of sample size? It seems from checking by putting in identical parameters as x, y that max(TIC) = 16 for 100 datapoints and max(TIC) = 148 for 1000 datapoints. Don't know how to derive this though, should depend also on c parameter and how the algorithm is approximating the true matrix?.}

@@

\textcolor{red}{Maybe it will be better to combine the two traces? Can have tour from V1-V2 to V3-V4 to V5-V6, indicate position of V3-V4 in path, will save space, make direct comparison easier.}

@@

\begin{table}
\begin{center}
\caption{Summary}
\label{tab:summary}
\begin{tabular}{|l|c|c|c|c|c|c|}
\hline
Index & smooth & squintability & flexible & rotation invariant & speed \\
\hline
Convex & ! & ! & ! & ! & \checkmark \\
Skinny & ! & !& ! & ! & \checkmark \\
Stringy & $\times$ & $\times$ & ! & ! & \checkmark \\
\hline
splines2D & \checkmark & \checkmark & ! & $\times$ & \checkmark \\
dcor2D & \checkmark & \checkmark & ! & $\times$ & ! \\
\hline
MINE & ! & \checkmark  & \checkmark & ! & ! \\
\hline
\end{tabular}
\end{center}
\end{table}
